---
title: "AnalysisPipelineMediod"
author: "Kevin Shin"
date: "5/11/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
tidytext dplyr stringr tokenizers gutenbergr rapportools textstem text2vec stopwords TDA philentropy lsa quanteda qlcMatrix irlba tm stringi utf8 cluster knitr

```{r cars}
library(tidytext)
library(dplyr)
library(stringr)
library(tokenizers)
library(gutenbergr)
library(rapportools)
library(textstem)
library(text2vec)
library(stopwords)
library(TDA)
library(philentropy)
library(lsa)
library(quanteda)
library(qlcMatrix)
library(irlba)
library(tm)
library(stringi)
library(utf8)
library(cluster)
```

###Load in Data
```{r}
gutenberg_filtered <- gutenberg_metadata %>% filter(is.na(author)==FALSE) %>% filter(is.na(title)==FALSE) %>% filter(has_text == TRUE) %>%  filter(rights == "Public domain in the USA.") %>% filter(language == "en")
topics <- c("Children's Fiction", "Humor", "Science Fiction", "Adventure", "Biographies")
```

###Selecting categories
```{r}
#returns vector of gutenbergIDs associated with that topic
isolateIDs <- function(category){
  subsetBookshelf <- gutenberg_filtered[grep(category, gutenberg_filtered$gutenberg_bookshelf),]
  #On May 11, gutenberg_id 2149 was not available on any mirror for download on gutenbergr
  subsetBookshelf <- subsetBookshelf$gutenberg_id[subsetBookshelf$gutenberg_id != 24450]
  subsetBookshelf <- subsetBookshelf[subsetBookshelf != 19513]
  subsetBookshelf <- subsetBookshelf[subsetBookshelf != 19515]
  subsetBookshelf <- subsetBookshelf[subsetBookshelf != 19526]
  subsetBookshelf <- subsetBookshelf[subsetBookshelf != 4290]
  subsetBookshelf <- subsetBookshelf[1:100]
  subsetBookshelf <- subsetBookshelf[!is.na(subsetBookshelf)]
  return(subsetBookshelf)
}
```

```{r}
set.seed(471)

children <- isolateIDs("Children's Fiction")
humor <- isolateIDs("Humor")
scifi <- isolateIDs("Science Fiction")
adventure <- isolateIDs("Adventure")
biographies <- isolateIDs("Biographies")

bookIndexing <- c(length(children), length(humor), length(scifi), length(adventure), length(biographies))
#print(min(bookIndexing))
#returns 47

children <- sample(children, 45, replace=FALSE, prob=NULL)
humor <- sample(humor, 45, replace=FALSE, prob=NULL)
scifi <- sample(scifi, 45, replace=FALSE, prob=NULL)
adventure <- sample(adventure, 45, replace=FALSE, prob=NULL)
biographies <- sample(biographies, 45, replace=FALSE, prob=NULL)

bookList <- c(children, humor, scifi, adventure, biographies)
bookList <- c(293,836,7862,8732,7006,5348,3429,530,7831,3785,998,11565,4660,3653,8670,874,11609,11602,9745,5623,2805,5417,5828,5075,6461,10340,1573,7493,770,3674,7037,3811,11151,528,296,7229,5747,5696,11111,5207,8679,399,646,10724,7124,2183,8713,22518,23338,6837,13647,9449,13872,24313,13993,6984,6768,6985,7464,13650,6836,4064,7298,6927,20633,22145,6840,4020,21427,23783,8176,2005,8931,3425,6879,20532,13648,24018,18881,4075,972,7833,8178,22689,4729, 14667, 11138,  2607,  4682, 14684,  7250, 10662,    84,   36,  7246,  7248, 18151,   605,    42, 13944,  7052,  9194, 11696,   551,    68,   159,   552,  8673, 17355,   123,   553,   149, 18137,  6585, 11870,  1329,  6903,  9862,  1607,  7401, 12901,  3479,  2488,   369,    86,  7244,    96,  1250,  6717,   604, 17958,  7242, 18109,   126,  1951,  2759,  5174, 18970,   558,    60, 2166,  5194,   103,  2710,  1690,  5745,  1259, 19307,  1724,  5746,   559, 10422,   848,  1947,    78,  2681, 24920,  2713,  5315,    92,  1257,  1184,   589,   421,  2785, 27525,  1752,  6751,711, 1965,    85,  3526,  1145, 10743,  1711,  2727,  6769,  2609,   106,  2226, 16965, 45456, 19767,   590, 12406, 14555,   813, 16469, 10598,  1702, 21091,  4689, 12014,  1265,  9069, 21677,20733,  4667,   412, 12090, 45532, 14392, 13888,  2563,  6312,  2082,   529, 12985, 12984,  4691, 14992, 20439,  4690, 22345,  6702, 10622, 18757,  4693, 17388, 14004, 10986,  8770,  2447,  3029, 539)


```

###Approach 2

Computer 1: Wasserstein, p=1, then run similarity on mahattan
Computer 2: Wasserstein, p=1, then run similarity on euclidean
Computer 3: Bottleneck, then run similairty on manhattan
Computer 4: Bottleneck, then run similarity on euclidean

###Computer 1
```{r}
collection <- bookList
clusteringPD <- function(numLines){
  similarityMatrix <- matrix(ncol = length(collection), nrow = length(collection))
  diag(similarityMatrix) <- 0
  for (bookIndexHoriz in 1:length(collection)){
    for (bookIndexVert in 1:length(collection)){
      if (bookIndexVert > bookIndexHoriz){
        bookDTM <- computeDTM(collection[bookIndexVert],numLines)
        otherBookDTM <- computeDTM(collection[bookIndexHoriz],numLines)
        if (!is.null(bookDTM) && !is.na(otherBookDTM)){  
          bookDistanceMatrix <- makeDistanceMatrix(bookDTM)
          otherBookDistanceMatrix <- makeDistanceMatrix(otherBookDTM)
          Diag <- ripsDiag(X = bookDistanceMatrix,
                           maxdimension = 1,
                           maxscale = 100,
                           dist = "arbitrary", 
                           library = "Dionysus",
                           printProgress = FALSE, 
                           location=TRUE)
          DiagOther <- ripsDiag(X = otherBookDistanceMatrix,
                           maxdimension = 1,
                           maxscale = 100,
                           dist = "arbitrary", 
                           library = "Dionysus",
                           printProgress = FALSE, 
                           location=TRUE)
          wassersteinDist <- wasserstein(Diag[["diagram"]], DiagOther[["diagram"]], p = 1, dimension = 1)
          similarityMatrix[bookIndexHoriz,bookIndexVert] <- wassersteinDist
        }
      }
      else {
        similarityMatrix[bookIndexHoriz,bookIndexVert] <- 0
      }
    }
  }
  mainMatrix <- similarityMatrix + t(similarityMatrix)
  toReturn <- as.data.frame(mainMatrix)
  colnames(toReturn) <- collection
  rownames(toReturn) <- collection
  return(toReturn)
  
}
```


```{r}
similarityTable <- clusteringPD(200)
pamx <- pam(similarityTable, 5, diss = FALSE, cluster.only = FALSE, metric = "manhattan")
```


###Computer 2
```{r}
collection <- bookList
clusteringPD <- function(numLines){
  similarityMatrix <- matrix(ncol = length(collection), nrow = length(collection))
  diag(similarityMatrix) <- 0
  for (bookIndexHoriz in 1:length(collection)){
    for (bookIndexVert in 1:length(collection)){
      if (bookIndexVert > bookIndexHoriz){
        bookDTM <- computeDTM(collection[bookIndexVert],numLines)
        otherBookDTM <- computeDTM(collection[bookIndexHoriz],numLines)
        if (!is.null(bookDTM) && !is.na(otherBookDTM)){  
          bookDistanceMatrix <- makeDistanceMatrix(bookDTM)
          otherBookDistanceMatrix <- makeDistanceMatrix(otherBookDTM)
          Diag <- ripsDiag(X = bookDistanceMatrix,
                           maxdimension = 1,
                           maxscale = 100,
                           dist = "arbitrary", 
                           library = "Dionysus",
                           printProgress = FALSE, 
                           location=TRUE)
          DiagOther <- ripsDiag(X = otherBookDistanceMatrix,
                           maxdimension = 1,
                           maxscale = 100,
                           dist = "arbitrary", 
                           library = "Dionysus",
                           printProgress = FALSE, 
                           location=TRUE)
          wassersteinDist <- wasserstein(Diag[["diagram"]], DiagOther[["diagram"]], p = 1, dimension = 1)
          similarityMatrix[bookIndexHoriz,bookIndexVert] <- wassersteinDist
        }
      }
      else {
        similarityMatrix[bookIndexHoriz,bookIndexVert] <- 0
      }
    }
  }
  mainMatrix <- similarityMatrix + t(similarityMatrix)
  toReturn <- as.data.frame(mainMatrix)
  colnames(toReturn) <- collection
  rownames(toReturn) <- collection
  return(toReturn)
  
}
```

```{r}
similarityTable <- clusteringPD(100)
pamx <- pam(similarityTable, 5, diss = FALSE, cluster.only = FALSE, metric = "manhattan")
```




###Computer 3
```{r}
collection <- bookList
clusteringPD <- function(numLines){
  similarityMatrix <- matrix(ncol = length(collection), nrow = length(collection))
  diag(similarityMatrix) <- 0
  for (bookIndexHoriz in 1:length(collection)){
    for (bookIndexVert in 1:length(collection)){
      if (bookIndexVert > bookIndexHoriz){
        bookDTM <- computeDTM(collection[bookIndexVert],numLines)
        otherBookDTM <- computeDTM(collection[bookIndexHoriz],numLines)
        if (!is.null(bookDTM) && !is.na(otherBookDTM)){  
          bookDistanceMatrix <- makeDistanceMatrix(bookDTM)
          otherBookDistanceMatrix <- makeDistanceMatrix(otherBookDTM)
          Diag <- ripsDiag(X = bookDistanceMatrix,
                           maxdimension = 1,
                           maxscale = 100,
                           dist = "arbitrary", 
                           library = "Dionysus",
                           printProgress = FALSE, 
                           location=TRUE)
          DiagOther <- ripsDiag(X = otherBookDistanceMatrix,
                           maxdimension = 1,
                           maxscale = 100,
                           dist = "arbitrary", 
                           library = "Dionysus",
                           printProgress = FALSE, 
                           location=TRUE)
          bottleDist <- bottleneck(Diag[["diagram"]], DiagOther[["diagram"]], p = 1, dimension = 1)
          similarityMatrix[bookIndexHoriz,bookIndexVert] <- bottleDist
        }
      }
      else {
        similarityMatrix[bookIndexHoriz,bookIndexVert] <- 0
      }
    }
  }
  mainMatrix <- similarityMatrix + t(similarityMatrix)
  toReturn <- as.data.frame(mainMatrix)
  colnames(toReturn) <- collection
  rownames(toReturn) <- collection
  return(toReturn)
  
}
```

```{r}
similarityTable <- clusteringPD(100)
pamx <- pam(similarityTable, 5, diss = FALSE, cluster.only = FALSE, metric = "euclidean")
```



###Computer 4
```{r}
collection <- bookList
clusteringPD <- function(numLines){
  similarityMatrix <- matrix(ncol = length(collection), nrow = length(collection))
  diag(similarityMatrix) <- 0
  for (bookIndexHoriz in 1:length(collection)){
    for (bookIndexVert in 1:length(collection)){
      if (bookIndexVert > bookIndexHoriz){
        bookDTM <- computeDTM(collection[bookIndexVert],numLines)
        otherBookDTM <- computeDTM(collection[bookIndexHoriz],numLines)
        if (!is.null(bookDTM) && !is.na(otherBookDTM)){  
          bookDistanceMatrix <- makeDistanceMatrix(bookDTM)
          otherBookDistanceMatrix <- makeDistanceMatrix(otherBookDTM)
          Diag <- ripsDiag(X = bookDistanceMatrix,
                           maxdimension = 1,
                           maxscale = 100,
                           dist = "arbitrary", 
                           library = "Dionysus",
                           printProgress = FALSE, 
                           location=TRUE)
          DiagOther <- ripsDiag(X = otherBookDistanceMatrix,
                           maxdimension = 1,
                           maxscale = 100,
                           dist = "arbitrary", 
                           library = "Dionysus",
                           printProgress = FALSE, 
                           location=TRUE)
          bottleDist <- bottleneck(Diag[["diagram"]], DiagOther[["diagram"]], p = 1, dimension = 1)
          similarityMatrix[bookIndexHoriz,bookIndexVert] <- bottleDist
        }
      }
      else {
        similarityMatrix[bookIndexHoriz,bookIndexVert] <- 0
      }
    }
  }
  mainMatrix <- similarityMatrix + t(similarityMatrix)
  toReturn <- as.data.frame(mainMatrix)
  colnames(toReturn) <- collection
  rownames(toReturn) <- collection
  return(toReturn)
  
}
```

```{r}
similarityTable <- clusteringPD(100)
pamx <- pam(similarityTable, 5, diss = FALSE, cluster.only = FALSE, metric = "manhattan")
```

